MSE for rank_1 simulation

### 2018-01-27 analysis/MSErank3sim.Rmd
Files commited by wflow_commit.

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          plot.title = element_text(size = 18, face = "bold"),
          axis.text.y = element_text(size =15), 
          axis.text.x = element_text(size =15,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/simulation/rankthree/boxplot.rds")
colnames(sparse_res) = c("PMD.cv1","flash","flash.pn","SVD","SSVD","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
p3 = plot_res(sparse_diff,title = "Rank 3 example",methods_name = methods_name)
```

>>>>

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name,myColors){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+ scale_color_manual(values=myColors)+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          plot.title = element_text(size = 18, face = "bold"),
          axis.text.y = element_text(size =15), 
          axis.text.x = element_text(size =15,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/output/simulation/rankthree/boxplot.rds")
colnames(sparse_res) = c("PMD.cv1","flash","flash.pn","SVD","SSVD","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
fill_color =  c("red","yellow3", "springgreen", "springgreen3", "cyan","cyan3", "deepskyblue","violet","purple")
p3 = plot_res(sparse_diff,title = "Rank 3 example",methods_name = methods_name,
              myColors = fill_color[c(1,2,3,7,8,9)])
```
